Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-05-16 src/tex/ms.tex
Manuscript updates

The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars. As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$. We investigate this prediction further here.

>>>>

The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars born in-situ in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars. As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$. We investigate this prediction further here.
